D.I.A.G.R.A.M.: Development of Image Analysis for Graph Recognition And Modeling

### 2025-06-29 doc/article/article.tex
Updated paper

\subsubsection{Text Digitization}
Since the task of converting an image of text into the relative string has already been solved in various ways, we settled upon the Microsoft \textit{Trocr Handwritten} Transformer model; more precisely, the \textit{base} version of it. Every bounding box containing text that has been found is later passed to the model, and the resulting string generated by the model is linked to it.\\

@@

The solution, as stated before, was to

@@

\bibliographystyle{IEEEtran}
\bibliography{article}

@@

\section{Double Clustering}
\label{double_clustering}
The first algorithmic approach proposed to solve this task - called \textit{Double Clustering} - was as follows: 
\begin{enumerate}
	\item Apply a clustering algorithm to the bounding box.
	\item Suppose that the biggest cluster belongs to the arrow; the other clusters are thought to contain useless elements for this task, and can be discarded.
	\item Find the keypoints of the arrow using SIFT.
	\item Find the two keypoints inside the arrow with maximum distance. Assume that these two points are closely related to the two ends of the arrow.
	\item Run a template matching procedure inside the two clusters to find the head of the arrow.
\end{enumerate}

For Step (1), we tried to employ both Spectral Clustering (see Figure~\ref{fig:spectral_clustering}) and DBSCan (see Figure~\ref{fig:arrow_double_clustering_clusters}).

@@

For Step (3), we used SIFT in order to find keypoints and some descriptors for them - necessary for the later template matching.
During Step (4), we were able to correctly deduce the overall direction of the arrow (see Figure~\ref{fig:arrow_double_clustering_direction}).

>>>>

\subsubsection{Text Digitization}
Since the task of converting an image of text into the relative string has already been solved in various ways, we settled upon the Microsoft \textit{Trocr Handwritten} Transformer model; more precisely, the \textit{base} version of it \cite{microsofttrocr}. Every bounding box containing text that has been found is later passed to the model, and the resulting string generated by the model is linked to it.\\

@@

The solution, as stated before, was to finetune the already working RCNN in order for it to also extract the bounding boxes of both tails and heads of the arrow.

@@

\bibliographystyle{IEEEtran}

\newpage
\bibliography{article}
\newpage

@@

\section{Double Clustering}
\label{double_clustering}
The first algorithmic approach proposed to solve this task - called \textit{Double Clustering} - was as follows: 
\begin{enumerate}
	\item Apply a clustering algorithm to the bounding box.
	\item Suppose that the biggest cluster belongs to the arrow; the other clusters are thought to contain useless elements for this task, and can be discarded.
	\item Find the keypoints of the arrow using SIFT \cite{SIFT}.
	\item Find the two keypoints inside the arrow with maximum distance. Assume that these two points are closely related to the two ends of the arrow.
	\item Run a template matching procedure inside the two clusters to find the head of the arrow.
\end{enumerate}

For Step (1), we tried to employ both Spectral Clustering (see Figure~\ref{fig:spectral_clustering}) and DBScan \cite{dbscan} (see Figure~\ref{fig:arrow_double_clustering_clusters}).

@@

For Step (3), we used SIFT \cite{SIFT} in order to find keypoints and some descriptors for them - necessary for the later template matching.
During Step (4), we were able to correctly deduce the overall direction of the arrow (see Figure~\ref{fig:arrow_double_clustering_direction}).
